Arbitrary Precision and Arbitrary $n$-Grams

### 2011-03-01 paper/paper.Rnw
move

\newcommand\ngram{$n$-gram}
\newcommand\loga{logarithmic arithmetic}

@@

		Our hypothesis was that the arbitrary precision math would reveal a
		small amount of error in computing the perplexity logarithmically.  Our
		results seem to indicate that any such error is very small (differing
		only in the last digit in measuring the perplexity of whole corpora),
		but that arbitrary-precision mathematics is much slower than floating
		point mathematics with logs when finding the product of many numbers.
		See table \ref{runtimes}.  This suggests that the logarithmic
		computation is indeed an accurate way to compute perplexity,
		particularly in light of the more than \osn{10}-fold speed improvements
		it results in.

@@

\section*{Experimental design}
We trained our model on the training data and then
ran two experiments to study the effect of \ngram length and
probability computation type on perplexity on the two corpora.
The two probability computation types were arbitrary precision
arithmetic and \loga.
For each experiment, we tested \ngram length of $n$=$1$ to $5$.

@@

>>>>

@@

@@

\section*{Experimental design}
We trained our model on the training data and then
ran two experiments to study the effect of $n$-gram length and
probability computation type on perplexity on the two corpora.
The two probability computation types were arbitrary precision
arithmetic and logarithmic arithmetic.
For each experiment, we tested $n$-gram length of $n$=$1$ to $5$.

@@

\subsection*{Arbitrary precision arithmetic}
		Our hypothesis was that the arbitrary precision math would reveal a
		small amount of error in computing the perplexity logarithmically.  Our
		results seem to indicate that any such error is very small (differing
		only in the last digit in measuring the perplexity of whole corpora),
		but that arbitrary-precision mathematics is much slower than floating
		point mathematics with logs when finding the product of many numbers.
		See table \ref{runtimes}.  This suggests that the logarithmic
		computation is indeed an accurate way to compute perplexity,
		particularly in light of the more than \osn{10}-fold speed improvements
		it results in.
